Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\extraspacing {\underline{\em Example 4.5.} Recall from Example 4.3 that rectangle $\alpha'$ serve as both $\gbot(\bm{t}_1)$ and $\gbot(\bm{t}_2)$. Thus, $\maxtop(\alpha') = \max\{\ytop(B_{\bm{t}_1}),$ $\ytop(B_{\bm{t}_2})\} = \max\{6, 9.5\} = 9.5$. The top-sliced rectangle of $r'$ is the rectangle $\alpha^*$ in Figure~\ref{fig:hv:type1:ex}d. Rectangles $\beta'_1$ and $\beta'_2$ do not have top-sliced rectangles.
\qed

>>>>

\extraspacing {\underline{\em Example 4.5.} Recall from Example 4.3 that rectangle $\alpha'$ is both $\gbot(\bm{t}_1)$ and $\gbot(\bm{t}_2)$. Thus, $\maxtop(\alpha') = \max\{\ytop(B_{\bm{t}_1}),$ $\ytop(B_{\bm{t}_2})\} = \max\{6, 9.5\} = 9.5$. The top-sliced rectangle of $\alpha'$ is the rectangle $\alpha^*$ in Figure~\ref{fig:hv:type1:ex}d. Rectangles $\beta'_1$ and $\beta'_2$ do not have top-sliced rectangles.
\qed
